An Elaboration on\\Order-Adaptive Regularisation for Variational Optical Flow:\\Global, Local and in Between

### 2018-08-06 seminar_vof/paper/paper.tex
sum more stuff
adaptive schemes completed

To get to this behavior of $c$ from the euler lagrange equation's point of view, the corresponding selection term $\phi_\lambda(c)$ has to be found.
By examining the regularizers partial derivative $\frac{\partial R}{\partial c} = 0$ we get to the following equation.
\begin{flalign}
\frac{\partial R(\flow,c)}{\partial c} = &\int_\Omega S_1(\flow) - S_2(\flow,\aaux,\baux) + \phi_\lambda'(c) \;d\x \;=\; 0
&&\nonumber\\
-\phi_\lambda'(c)*|\Omega| = &\int_\Omega S_1(\flow) - S_2(\flow,\aaux,\baux) \;d\x
&&\nonumber\\
\label{eq:deriv_r_to_c}
\phi_\lambda'(c) = \frac{1}{|\Omega|}&\int_\Omega S_2(\flow,\aaux,\baux) - S_1(\flow) \;d\x
&&
\end{flalign}
The right hand side of \cref{eq:deriv_r_to_c} also occurs in \cref{eq:c} which can be reformulated as follows in order to be plugged in.
\begin{flalign}
&\frac{1}{|\Omega|}\int_\Omega S_2 - S_1\;d\x = \Delta-T
%&&\nonumber\\
\quad\text{with}\quad
\Delta = -\lambda*\ln(\frac{1}{c}-1)
&&\nonumber\\\label{eq:phi'}
&\phi_\lambda'(c) = -\lambda*\ln\Big(\frac{1}{c}-1\Big) - T
\end{flalign}
To obtain $\phi_\lambda$ we integrate both sides of \cref{eq:phi'} and get the following selection term with integration constant $C$.
\begin{flalign}
\phi_\lambda(c) = \lambda \Bigg( \ln(1-c)-c*\ln\Big(\frac{1}{c}-1\Big) \Bigg) -Tc + C &&
\end{flalign}
When chosing $C=T$ we can get a more intuitive formulation of the regularizer, using a cleverly tailored replacement $\phi$ for $\phi_\lambda$.
\begin{flalign}\label{eq:phi}
\phi(c) = \frac{\phi_\lambda(c) + T*(c-1)}{\lambda} &= \ln(1-c)-c*\ln\Big(\frac{1}{c}-1\Big)
&&\\
%= \ln(1-c)-c*\ln\Big(\frac{1-c}{c}\Big) 
& = c*\ln(c) + (1-c)*\ln(1-c)
%-c ln(1/c -1 ) = -c ln((1-c)/c) = -c ln(1-c) + c ln(c)
&&\nonumber\\
R(\flow,c) = \int_\Omega \inf_{\aaux,\baux}\big[\; c*S_1(\flow) 
& + (1-c)*\big(S_2(\flow,\aaux,\baux) +T\big)
&&\\
& + \beta*S_\text{aux}(\aaux,\baux)
+ \lambda*\phi(c)\;\big] \;d\x \nonumber&&
\end{flalign} 
In this representation the threshold parameter $T$ appears in the convex combination together with $S_2$ and can be interpreted as an extra cost to be paid in order to use second order regularization.
The sigmoid slope parameter $\lambda$ now works as a weight for the selection term $\phi$ which has become independent of $\lambda$.
In fact the selection term has simplified quite a bit and it can be seen that it is a symmetric function which is also illustarted in \cref{fig:c_phi}.
From the figure it can also be seen that $\phi$ is minimal for $c=\frac{1}{2}$ which can be interpreted as a prior on $c$ for when the model is indecisive on regularization order.
So by definition of $\phi$ neither of the regularizers is preferred, but due to the threshold $T$ the descision is biased towards the first order regularization.

@@

\subsection{Non-Local Scheme}
Since the local scheme allows for different regularization order per pixel based on a decision which only takes that pixels location into account, regularization order may fluctuate a lot in this model.
To make the descision more consistent with the pixels neighorhood, the weighting function $c_{\text{local}}(\x)$ is altered to
take a rectangular shaped patch of pixels around it into account.
\begin{flalign}
\cNl(\x) = \frac{1}{|\patch(\x)|}\int_{\patch(\x)}\cnl(\y)\;d\y 
&&\\
R_\text{nl}(\flow,\cnl) = \int_\Omega \inf_{\aaux,\baux}\big[\; \cNl*S_1(\flow) 
& + (1-\cNl)*\big(S_2(\flow,\aaux,\baux) +T\big)
&&\\
& + \beta*S_\text{aux}(\aaux,\baux)
+ \lambda*\phi(\cnl)\;\big] \;d\x \nonumber&&
\end{flalign}
Here $\mathcal{N}(\x)$ denotes the patch of $\x$ and $|\mathcal{N}(\x)|$ the patch size which is used for normalization.
To find $\cnl$, $R_\text{nl}(\flow,\cnl)$ is minimized with respect to it.
\begin{flalign}
\frac{\partial R(\flow,\cnl)}{\partial \cnl} = \cdots
&&\\
\text{derivation of~} \cnl \dots
&&\\
\cnl = \cdots
&&
\end{flalign}

\subsection{Region-Based Scheme}
The non-local scheme takes a neighborhood around a pixel into account for the descision on regularization order.
To push it yet a little further, the region based scheme decides on order leveraging a level set function $z(\x):\Omega\to\mathbb{R}$ which devides the image space into first and second order regularized regions.
The corresponding regularizer reads as follows.
\begin{flalign}
&R(\flow,z) = \int_\Omega c_\text{rgn}(z)*S_1 + (1-c_\text{rgn}(z))*(S_2 + T) + \theta*|\nabla c_\text{rgn}(z)| \;d\x
&&\\
&c_\text{rgn}(z) = \frac{1}{1+e^{z/\lambda}}
&&
\end{flalign}
Here $c_\text{rgn}$ is as well a sigmoid function, but choosen to approximate the heaviside funtion ($\lambda\to 0$) in order to obtain hard boundaries for the regions defined by $z$.
The selection term from the previous schemes has been replaced by a smoothness term on $c_\text{rgn}$ which penalizes level set functions with lots of sign changes.
Due to this penalization short paths for $z(\x)=0$ are favored resulting in smooth region boundaries.

@@

\bibliographystyle{abbrv}
%% use following if all content of bibtex file should be shown
% \nocite{*}
\bibliography{literatur}
\end{document}

>>>>

To get to this behavior of $c$ from the euler lagrange equation's point of view, the corresponding selection term $\phi_\lambda(c)$ has to be found.
By examining the regularizers partial derivative $\frac{\partial R}{\partial c} = 0$ we get to the following equation.
\begin{flalign}
\frac{\partial R(\flow,c)}{\partial c} = &\int_\Omega S_1(\flow) - S_2(\flow,\aaux,\baux) + \phi_\lambda'(c) \;d\x \;=\; 0
&&\nonumber\\
-\phi_\lambda'(c)*|\Omega| = &\int_\Omega S_1(\flow) - S_2(\flow,\aaux,\baux) \;d\x
&&\nonumber\\
\label{eq:deriv_r_to_c}
\phi_\lambda'(c) = \frac{1}{|\Omega|}&\int_\Omega S_2(\flow,\aaux,\baux) - S_1(\flow) \;d\x
&&
\end{flalign}
The right hand side of \cref{eq:deriv_r_to_c} also occurs in \cref{eq:c} which can be reformulated as follows in order to be plugged in.
\begin{flalign}
&\frac{1}{|\Omega|}\int_\Omega S_2 - S_1\;d\x = \Delta-T
%&&\nonumber\\
\quad\text{with}\quad
\Delta = -\lambda*\ln(\frac{1}{c}-1)
&&\nonumber\\\label{eq:phi'}
&\phi_\lambda'(c) = -\lambda*\ln\Big(\frac{1}{c}-1\Big) - T
\end{flalign}
To obtain $\phi_\lambda$ we integrate both sides of \cref{eq:phi'} and get the following selection term with integration constant $C$.
\begin{flalign}
\phi_\lambda(c) = \lambda \Bigg( \ln(1-c)-c*\ln\Big(\frac{1}{c}-1\Big) \Bigg) -Tc + C &&
\end{flalign}
When chosing $C=T$ we can get a more intuitive formulation of the regularizer, using a cleverly tailored replacement $\phi$ for $\phi_\lambda$.
\begin{flalign}\label{eq:phi}
\phi(c) = \frac{\phi_\lambda(c) + T*(c-1)}{\lambda} &= \ln(1-c)-c*\ln\Big(\frac{1}{c}-1\Big)
&&\\
%= \ln(1-c)-c*\ln\Big(\frac{1-c}{c}\Big) 
& = c*\ln(c) + (1-c)*\ln(1-c)
%-c ln(1/c -1 ) = -c ln((1-c)/c) = -c ln(1-c) + c ln(c)
&&\nonumber\\
R(\flow,c) = \int_\Omega \inf_{\aaux,\baux}\big[\; c*S_1(\flow) 
& + (1-c)*\big(S_2(\flow,\aaux,\baux) +T\big)
&&\\
& + \beta*S_\text{aux}(\aaux,\baux)
+ \lambda*\phi(c)\;\big] \;d\x \nonumber&&
\end{flalign} 
In this representation the threshold parameter $T$ appears in the convex combination together with $S_2$ and can be interpreted as an extra cost to be paid in order to use second order regularization.
The sigmoid slope parameter $\lambda$ now works as a weight for the selection term $\phi$ which has become independent of $\lambda$.
In fact the selection term has simplified quite a bit and it can be seen that it is a symmetric function which is illustarted in \cref{fig:c_phi}.
From the figure it can also be seen that $\phi$ is minimal for $c=\frac{1}{2}$ which can be interpreted as a prior on $c$ for when the model is indecisive on regularization order.
So by definition of $\phi$ neither of the regularizers is preferred, but due to the threshold $T$ the descision is biased towards the first order regularization.

@@

\subsection{Non-Local Scheme}
Since the local scheme allows for different regularization order per pixel based on a decision which only takes that pixels location into account, regularization order may fluctuate a lot in this model.
To make the descision more consistent with the pixels neighorhood, the weighting function $c_{\text{local}}(\x)$ is altered to
take a rectangular shaped patch of pixels around it into account.
\begin{flalign}
\cNl(\x) = \frac{1}{|\patch(\x)|}\int_{\patch(\x)}\cnl(\y)\;d\y 
&&\\
R_\text{nl}(\flow,\cnl) = \int_\Omega \inf_{\aaux,\baux}\big[\; \cNl*S_1(\flow) 
& + (1-\cNl)*\big(S_2(\flow,\aaux,\baux) +T\big)
&&\\
& + \beta*S_\text{aux}(\aaux,\baux)
+ \lambda*\phi(\cnl)\;\big] \;d\x \nonumber&&
\end{flalign}
Here $\mathcal{N}(\x)$ denotes the patch of $\x$ and $|\mathcal{N}(\x)|$ the patch size which is used for normalization.
To find $\cnl$, $R_\text{nl}(\flow,\cnl)$ is minimized with respect to it and yields:
\begin{flalign}
\cnl(\y) = \frac{1}{1+e^{\Delta(\y)/\lambda}} \quad\text{with}\quad \Delta(\y) = \int_{\mathcal{N}(\y)} \frac{ T + S_2 - S_1 }{|\mathcal{N}(\x)|} \;d\x
&&
\end{flalign}
It may be surprising at first that the integrated $\cnl$ itself contains a nested integral, but it is easy to convince yourself when thinking about a 
discrete version $c_{\x}$.
When taking the derivative with respect to a single $c_{\x}$, then due to the integral in $\cNl$ we need to identify all terms which contain $c_{\x}$ (which is defined by the patch $\mathcal{N}(\x)$).
The reason for normalization $\frac{1}{|\mathcal N(\x) |}$ being inside the integral is that patches at the boundaries vary in size (become smaller as less pixels are defined there).

\subsection{Region-Based Scheme}
The non-local scheme takes a neighborhood around a pixel into account for the descision on regularization order.
To push it yet a little further, the region based scheme decides on order leveraging a level-set function $z(\x):\Omega\to\mathbb{R}$ which devides the image space into first and second order regularized regions.
Recall that a level-set function defines a closed curve (or curves) by $\{\x \;|\; z(\x)=0\}$ that defines the descision boundary.
The regions are thus defined by $\{\x \;|\; z(\x) < 0\}$ and $\{\x \;|\; z(\x) > 0\}$ which will be leveraged to regionally decide on regularization order.
The corresponding regularizer reads as follows.
\begin{flalign}
&R(\flow,z) = \int_\Omega c_\text{rgn}(z)*S_1 + (1-c_\text{rgn}(z))*(S_2 + T) + \theta*|\nabla c_\text{rgn}(z)| \;d\x
&&\\
&c_\text{rgn}(z) = \frac{1}{1+e^{z/\lambda}}
&&
\end{flalign}
Here $c_\text{rgn}$ is as well a sigmoid function, but choosen to approximate the heaviside funtion ($\lambda\to 0$) in order to obtain hard boundaries for the regions defined by $z$.
The selection term from the previous schemes has been replaced by a smoothness term on $c_\text{rgn}$ which penalizes non-smooth level set functions which results in less sign changes.
Due to this penalization short paths for $\{\x \;|\; z(\x)=0\}$ are favored resulting in smooth region boundaries.

Unfortunately this sophisticated scheme comes at a larger computational cost as $z$ has to be evolved due to its smoothenss term \cite{someone}.

\section{Experiments}
To evaluate this new approach, the authors conducted a few experiments which will be presented in this section.

@@

\bibliographystyle{abbrv}
%% use following if all content of bibtex file should be shown
% \nocite{*}
\bibliography{literatur}
\end{document}
\grid
